\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-08 doc/paper.tex
added reference to jae-hyeon's lattice method as a possible solution to convergence problems.

In addition modular design of FlexibleSUSY allows solver for the boundary

>>>>

In addition the modular design of FlexibleSUSY allows for the solver
for the boundary value problem to be replaced. An alternative solver
with better convergence properties (at the expense of slower speed) is
already planned for a later release.
